Plots for Latent Hawkes Paper

### 2020-10-26 output_scripts/Paper_Plots.Rmd
update fig 3 and set up sim for data from m1

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
                                         expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),
                    title = "(a)" )
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
#dev.off()
```
## Figure 3b: Ranking Comparison

@@

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
                    byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks_diff[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
           axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
      # curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
      #       ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
      # plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
      #      verticals = TRUE, col = "red", lwd = 2)
    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))

@@

>>>>

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
                                         expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]) )
                    # title = "(a)" )
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
#dev.off()
```
## Figure 3b: Ranking Comparison

@@

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
                    byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks_diff[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
           axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])

    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))

@@

```{r construct ks diff normalised by num events}
norm_diff <- (m2_ks - m1_ks)#/m1_ks
norm_diff[is.nan(norm_diff)] <- 0
count_mat <- matrix(0, nrow = mice_number, ncol = mice_number)

for(i in expert_rank_10[[current_cohort]]) {
  for(j in expert_rank_10[[current_cohort]]) {
    if( norm_diff[i,j] != 0 ) {
      num_events <- unique_pairs_df %>% 
      filter(initiator == i & recipient == j) %>%
      pull(count)
      # diff[i,j] <- diff[i,j] / num_events
      count_mat[i,j] <- num_events
    }
  }
}

tibble(diff_norm = as.vector(norm_diff),
       events = as.vector(count_mat)) %>%
  filter(events > 0 ) %>%
  ggplot(aes(events,diff_norm)) + geom_point() +
  ylab("M2-M1") +
  theme_minimal()

tibble(diff_norm = as.vector(norm_diff),
       events = as.vector(count_mat)) %>%
  filter(events > 0) %>%
  ggplot(aes(diff_norm)) + 
  geom_histogram() +
  theme_minimal()

```
```{r repeat for residuals}
m1_pr <- readRDS(paste(data_path,cohort_names[current_cohort],
                   "/chp_pr_matrix_",cohort_names[current_cohort],
                   ".RDS",sep=''))

tibble(m1pr = as.vector(m1_pr),
       m2pr = as.vector(m2_pr)) %>%
  mutate(diff = m2pr - m1pr) %>%
  ggplot(aes(diff)) + 
  geom_histogram() +
  labs(x = "M2 PR - M1 PR") +
  theme_minimal()

```{r compute mean decrease in ks-score}
summary(as.vector(m2_ks[m2_ks != 0]))
summary(as.vector(m1_ks[m1_ks != 0]))

t.test(as.vector(m2_ks[m2_ks != 0]), as.vector(m1_ks[m1_ks != 0]))

diff <- as.vector(m2_ks[m2_ks != 0]) - as.vector(m1_ks[m1_ks != 0])

length(which(diff < 0))/length(diff)
summary(diff)
```
